---
title: "Data on Complaints Against Law Enforcement"
output: html_document
date: "2022-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
pacman::p_load(tidyverse)
pacman::p_load(skimr)
pcd <-read.csv("policecomplaintsdata.csv")


```


One other possible correlation we'll be looking into is the relatinship between the race of the complainant and the race of the police officer.



```{r rolebyrade}


ggplot(pcd, mapping = aes(x =mos_ethnicity, fill = "red" ))+

geom_bar(mapping = aes(y = ..prop.., group = 1),color = "black", fill = "red")+

scale_y_continuous(labels = scales::percent_format(accuracy = 1))+

theme_light()+
  
xlab("Race of Police with Abuse Allegations")+

ylab("Proportion by Race")
```

As this graph depicts, the vast majority of complaints are made against white police officers.
```{r raceofcomplainants}
ggplot(pcd, mapping = aes(x =complainant_ethnicity ))+

geom_bar(mapping = aes(y = ..prop.., group = 1),color = "black", fill = "blue")+

scale_y_continuous(labels = scales::percent_format(accuracy = 1))+

theme_light()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  
xlab("Race of those who have filed Complaints")+

ylab("Proportion by Race")

```
As you can see from this graph, over 50% of those who file complaints against police identify as black, with about 20% identifying as Hispanic. The relationship between physical characteristics and police conduct will be further explored in the full paper.

```{r age_year}
pcd |>
  group_by(complainant_age_incident, fado_type) |>
  filter(complainant_age_incident > 0) |>
  ggplot(mapping = aes(x = fado_type, y = complainant_age_incident, fill = 'red')) +
  geom_boxplot() +
  theme_light() +
  theme(legend.position = 'none') +
  labs(x = "Type of Complaint", y = "Age of Complaint Filer")
  
  
```

